\begin{center}
  \large\textbf{ABSTRACT}
\end{center}

\addcontentsline{toc}{chapter}{ABSTRACT}

\vspace{2ex}

\begingroup
% Menghilangkan padding
\setlength{\tabcolsep}{0pt}

\noindent
\begin{tabularx}{\textwidth}{l >{\centering}m{3em} X}
  \emph{Name}     & : & Batrisyia Zahrani Ananto        \\

  \emph{Title}    & : & WHEELCHAIR MOVEMENT CONTROL WITH HEAD GESTURE
USING MEDIAPIPE BASED ON NUC   \\

  \emph{Advisors} & : & 1. Dr. Eko Mulyanto Yuniarno,S.T.,M.T.  \\
                  &   & 2. Dion Hayu Fandiantoro, S.T.,M.Eng. \\
\end{tabularx}
\endgroup

% Ubah paragraf berikut dengan abstrak dari tugas akhir dalam Bahasa Inggris
\emph{Quadriplegia or tetraplegia is paralysis that occurs in all four limbs. Because of their limitations, they need a wheelchair. Controlling the movement of a wheelchair can be a challenge, especially for users with significant physical limitations. It is necessary to develop a wheelchair control system that can be used by tetraplegic sufferers. One approach that can be taken to control a wheelchair is to extract facial features and detect head gesture using mediapipe. Then the classified head gesture data will be sent by the NUC to the wheelchair control system. This control system will regulate the direction of movement of the wheelchair. By using the methodology used, several conclusions can be drawn from the tests that have been carried out. The model that will be used has a 7 layer CNN architecture with Convolutional 2D 64, 256 and ending with Dense 512. The model distance with the highest accuracy is 50 centimeters. The light intensity with the highest accuracy is 110 lux. The FPS speed of the writer's laptop is higher than the NUC used. The average motor response time delay is 0.3025423729 seconds and the inference time is 0.07220 seconds. The average stability of the wheelchair motor for detection for 2 seconds is 8,9364 seconds.}

% Ubah kata-kata berikut dengan kata kunci dari tugas akhir dalam Bahasa Inggris
\emph{Keywords}: Control, Head Gesture, NUC, Tetraplegia, Wheelchair.
